---
title: "ModelReport"
author: "Xiuna Zhu"
date: "9/20/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Model Results
```{r message=TRUE, include=FALSE}
source('RStanModels.R')
source('dataana.R') 
models <- c("Bisection Model",  "Spacing Model", "Ensemble Mean",  "Two-stage Ensemble Mean", "EDA", "Bisection Model GM",  "Spacing Model GM", "Ensemble Mean GM",  "Two-stage Ensemble Mean GM", "EDA GM") 
expDat <- list(dat_exp1, dat_exp2, dat_exp3)

sub_exp_dat <- list()
for(modelname in models) {
  for (expID in 1: length(expDat)) {
    data_exp <- expDat[[expID]]
    data_exp$model <- modelname
    data_exp$Exp <- paste0('exp', expID)
    sub_exp <-  split(data_exp, data_exp$Exp) # split data for each subject
    sub_exp_dat <- list.append(sub_exp_dat, sub_exp[[1]])
  }
}
```

```{r}
#customize theme
theme_new <- theme_bw() + 
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line=element_line(colour="black"),
        strip.background = element_rect(color = "white", fill = "white"),
        panel.grid = element_blank())
```

### run the model on local computer

```{r include=FALSE}
if (runRstanModelslocally){
  rltlist <- list()
  for(i in 1: length(sub_exp_dat)){
    rlt <-  runRstanModelonlocal(sub_exp_dat[[i]])
    rltlist <- list.append(rltlist, rlt)
  }
  saveRDS(rltlist, file = paste0(getwd(), "/modelling/rlt_ALL.rds"))
}
```

## Model Results
```{r message=TRUE, include=FALSE}
models <- c("Bisection Model",  "Spacing Model", "Ensemble Mean",  "Two-stage Ensemble Mean", "EDA", "Bisection Model GM",  "Spacing Model GM", "Ensemble Mean GM",  "Two-stage Ensemble Mean GM", "EDA GM") 
expDat <- list(dat_exp1, dat_exp2, dat_exp3)
```

```{r}
sub_exp_dat <- list()
for(modelname in models) {
  for (expID in 1: length(expDat)) {
    data_exp <- expDat[[expID]]
    data_exp$model <- modelname
    data_exp$Exp <- paste0('exp', expID)
    sub_exp <-  split(data_exp, data_exp$Exp) # split data for each subject
    sub_exp_dat <- list.append(sub_exp_dat, sub_exp[[1]])
  }
}
```


### run the model on local computer

```{r include=FALSE}
if (runRstanModelslocally){
  rltlist <- list()
  for(i in 1: length(sub_exp_dat)){
    rlt <-  runRstanModelonlocal(sub_exp_dat[[i]])
    rltlist <- list.append(rltlist, rlt)
  }
  saveRDS(rltlist, file = paste0(getwd(), "/modelling/rlt_ALL.rds"))
}
```


### Merge the Result data 
To preprocess the model result data, we merge different model results as two csv files.

```{r}
AllresultList<- readRDS("modelling/rlt_ALL.rds") 
modelresults <- {}
thetalist <- {}
for(i in 1:length(AllresultList)){
  modelresults = rbind(modelresults, AllresultList[[i]]$result) 
  thetalist <- rbind(thetalist, AllresultList[[i]]$theta)
}
write.csv(modelresults, file.path(getwd(), "modelling/modelresults.csv"))
write.csv(thetalist, file.path(getwd(), "modelling/thetalist.csv"))
```

###load the data and remove the outliers

```{r}
par_observed <- read.csv('modelling/psy_quickpsy_observed.csv') %>% filter(!((NSub == 10|NSub == 6) & (cond == 'AF'| cond =='DF')))%>% filter(!((NSub == 1) & (cond == 'PS'| cond =='NS')))
modelresults<- read.csv("modelling/modelresults.csv")  %>% filter(!((NSub == 10|NSub == 6) & (cond == 'AF'| cond =='DF')))%>% filter(!((NSub == 1) & (cond == 'PS'| cond =='NS')))
```


### prediction of 'long' response

```{r}
pred_thetalist<- read.csv("modelling/thetalist.csv") 
pred_thetalist$X <-NULL
## probality of 'long' response for experiment 1, 2 and 3 
prob_exp <- read.csv('modelling/prob_exp.csv')
prob_exp$Dur = prob_exp$curDur
prob_exp$curDur <-NULL
prob_exp$obser_prob <-prob_exp$prob 
prob_exp$prob <-NULL


#combine oberserved and predicated probility
m_thetalist = left_join(pred_thetalist, prob_exp, by = c('NSub', 'cond', 'Dur')) 
m_thetalist$numParam = 6
m_thetalist[which(m_thetalist$model %in% c("Two-stage Ensemble Mean","Two-stage Ensemble Mean GM" )), "numParam"] = 9
m_thetalist[which(m_thetalist$model %in% c( "EDA", "EDA GM")), "numParam"] = 10
m_thetalist$err_prob = m_thetalist$Prob- m_thetalist$obser_prob
```


### prediction of PSE and JND
```{r}
#combine oberserved and predicated PSEs and JNDs
par_comb = left_join(modelresults, par_observed, by = c('NSub', 'cond')) 
par_comb$errpse <- par_comb$PSEmap-par_comb$pse
par_comb$errjnd <- par_comb$JNDmap-par_comb$jnd
par_comb$distance = sqrt(par_comb$errpse^2 + par_comb$errjnd^2)
head(par_comb)
```



### calculate distance to the observed Pses and Jnds
```{r}
m_parcomb <- par_comb %>% dplyr::group_by(model, cond) %>%
  dplyr::summarise(mPSEmap=mean(PSEmap),
                   pse = mean(pse), 
                   mJNDmap=mean(JNDmap),
                   jnd = mean(jnd),
                   merrpse =mean(errpse), 
                   merrjnd = mean(errjnd),n=n(), 
                   PSEmap_se = sd(PSEmap)/sqrt(n-1), 
                   JNDmap_se = sd(JNDmap)/sqrt(n-1),
                   errpse_se =sd(errpse)/sqrt(n-1), 
                   errjnd_se =sd(errjnd)/sqrt(n-1),
                   waic =mean(waic),
                   distance =mean(distance)) 
m_parcomb <- arrange(transform(m_parcomb,
                               cond=factor(cond,levels=c("PS","DF","U-shaped","NS","AF","I T-shaped"))),cond)
head(m_parcomb)
```
```{r}
mm_parcomb <- m_parcomb %>% dplyr::group_by(model) %>%
  dplyr::summarise(m_distance = mean(distance), waic = mean(waic))　 
mm_parcomb
```


###  Calculate the relative mean difference of two predictions of PSEs using AM and GM

```{r}
m_parcomb_new <- m_parcomb %>% dplyr::select(1:4)
m_parcomb_list <-split(m_parcomb_new, m_parcomb_new$model) 
par_model_list = NULL
for (i in 1: length(m_parcomb_list)){
  temp = m_parcomb_list[[i]]
  modelName = unique(temp$model)
  temp$model = NULL
  colnames(temp) = c('cond', paste0('mPSE_', modelName), 'pse')
  if(i == 1){
    par_model_list = temp
  }
  else{
    temp$pse = NULL
    par_model_list = left_join(par_model_list, temp, by=c("cond"))
  }
}
par_model_list$rmd_bisection =  abs(par_model_list$`mPSE_Bisection Model`-par_model_list$`mPSE_Bisection Model GM`)/par_model_list$pse
par_model_list$rmd_Spacing =  abs(par_model_list$`mPSE_Spacing Model`-par_model_list$`mPSE_Spacing Model GM`)/par_model_list$pse
par_model_list$rmd_Ensemble =  abs(par_model_list$`mPSE_Ensemble Mean`-par_model_list$`mPSE_Ensemble Mean GM`)/par_model_list$pse
par_model_list$rmd_Two_stage =  abs(par_model_list$`mPSE_Two-stage Ensemble Mean`-par_model_list$`mPSE_Two-stage Ensemble Mean GM`)/par_model_list$pse
par_model_list$rmd_EDA =  abs(par_model_list$`mPSE_EDA`-par_model_list$`mPSE_EDA GM`)/par_model_list$pse
#max(par_model_list$rmd_bisection ), max(par_model_list$rmd_Spacing), max(par_model_list$rmd_Ensemble),
max(  max(par_model_list$rmd_Two_stage), max(par_model_list$rmd_EDA))
```



### Display model results using arithmetic mean
```{r}
displayModellist <- c("Bisection Model",  "Spacing Model", "Ensemble Mean",  "Two-stage Ensemble Mean", "EDA")
par_comb <- par_comb %>% 
  filter(model %in% displayModellist)
par_comb<- arrange(transform(par_comb , model = factor(model, levels = displayModellist)), model)
par_comb <- arrange(transform(par_comb,      cond=factor(cond,levels=c("PS","DF","U-shaped","NS","AF","I T-shaped"))),cond)
```


```{r}
#calculate WAIC and MSE
mpar_comb <- par_comb %>% dplyr::group_by(model, cond) %>%
  dplyr::summarise( n=n(), mse_pse=sum((errpse)^2)/n,
                    mse_jnd=sum((errjnd)^2)/n, m_waic = mean(waic))
mpar_comb
```


## plot figure 7 in manuscript

```{r}
cbp1 <- c( "#CC79A7", "#F0E442", "#0072B2", "#E69F00", "#D55E00")
plt_ErrorScatter = ggplot(par_comb, aes(errpse, errjnd, color = model, shape = model)) + 
  geom_hline(yintercept = 0, linetype='dashed')+ geom_vline(xintercept = 0, linetype='dashed')+ 
  geom_point() +
  xlab('Prediction error in the PSEs (ms)')+ ylab('Prediction error in the JNDs (ms)')+
  scale_color_manual(values = cbp1) +
  scale_shape_manual(values=c(0, 1, 2, 8, 16))+
  facet_wrap(~cond)+
  theme_new+ theme(legend.position = 'top')

#ggsave(paste0("figures/fig7.png"), plt_ErrorScatter, width = 9, height=6)
ggsave("figures/fig7.tiff", units="in", width=9, height=6, dpi=300, compression = 'lzw')

plt_ErrorScatter
```


## plot figure 6 in manuscript

```{r}
m_par_observed <- par_observed %>% dplyr::group_by(cond) %>%
  dplyr::summarise(mpse=mean(pse), mjnd= mean(jnd), n=n(), 
                   pse_se =sd(pse)/sqrt(n-1), jnd_se =sd(jnd)/sqrt(n-1)) 
m_par_observed$mPSEmap<-m_par_observed$mpse 
m_par_observed$mJNDmap<-m_par_observed$mjnd 
```

```{r}

m_parcomb2 <- m_parcomb %>% 
  filter(model %in% displayModellist)
m_parcomb2<- arrange(transform(m_parcomb2 , model = factor(model, levels = displayModellist)), model)


fig_estimation = ggplot(m_parcomb2, aes(x=mPSEmap, y=mJNDmap, color = model, shape = model)) + 
  geom_point(data =m_par_observed, aes(x = mpse, y =mjnd, size=2), width =2, shape =16, alpha = 0.5,  color = 'black') +
  geom_point(data = par_comb, aes(x = pse, y =jnd), alpha = 0.25, color = 'lightgray', shape=16) +
  geom_point() +
  geom_errorbar(aes(ymax=mJNDmap+JNDmap_se, ymin=mJNDmap-JNDmap_se), size=0.6)+
  geom_errorbarh(aes(xmax=mPSEmap+PSEmap_se, xmin=mPSEmap-PSEmap_se),size=0.6)+
  ylab('Observed JNDs (ms)')+xlab('Observed PSEs (ms)') +
  scale_color_manual(values = cbp1) +
  scale_shape_manual(values=c(0, 1, 2, 8, 16))+
  theme_new+ theme(legend.position = 'top') + 
  facet_wrap(.~cond,  ncol=3)+
  scale_size(guide = 'none')

#ggsave("figures/fig6.png", fig_estimation, width = 9, height=6)
ggsave("figures/fig6.tiff", units="in", width=9, height=6, dpi=300, compression = 'lzw')
fig_estimation

```



