---
title: "ModelReport"
author: "Xiuna Zhu"
date: "9/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Model Results
```{r message=TRUE, include=FALSE}
source('RStanModels.R')
source('dataana.R') 
models <- c("Bisection Model",  "Spacing Model", "Ensemble Mean",  "Two-stage Ensemble Mean", "EDA", "Bisection Model GM",  "Spacing Model GM", "Ensemble Mean GM",  "Two-stage Ensemble Mean GM", "EDA GM") 
expDat <- list(dat_exp1, dat_exp2, dat_exp3)

sub_exp_dat <- list()
  for(modelname in models) {
    for (expID in 1: length(expDat)) {
      data_exp <- expDat[[expID]]
      data_exp$model <- modelname
      data_exp$Exp <- paste0('exp', expID)
      sub_exp <-  split(data_exp, data_exp$Exp) # split data for each subject
      sub_exp_dat <- list.append(sub_exp_dat, sub_exp[[1]])
    }
  }
```

### run the model on local computer

```{r include=FALSE}
if (runRstanModelslocally){
  rltlist <- list()
  for(i in 1: length(sub_exp_dat)){
     rlt <-  runRstanModelonlocal(sub_exp_dat[[i]])
     rltlist <- list.append(rltlist, rlt)
  }
  saveRDS(rltlist, file = paste0(getwd(), "/modelling/rlt_ALL.rds"))
}
```

## Model Results
```{r message=TRUE, include=FALSE}
models <- c("Bisection Model",  "Spacing Model", "Ensemble Mean",  "Two-stage Ensemble Mean", "EDA", "Bisection Model GM",  "Spacing Model GM", "Ensemble Mean GM",  "Two-stage Ensemble Mean GM", "EDA GM") 
expDat <- list(dat_exp1, dat_exp2, dat_exp3)
```

```{r}
  sub_exp_dat <- list()
  for(modelname in models) {
    for (expID in 1: length(expDat)) {
      data_exp <- expDat[[expID]]
      data_exp$model <- modelname
      data_exp$Exp <- paste0('exp', expID)
      sub_exp <-  split(data_exp, data_exp$Exp) # split data for each subject
      sub_exp_dat <- list.append(sub_exp_dat, sub_exp[[1]])
    }
  }
```


### run the model on local computer

```{r include=FALSE}
if (runRstanModelslocally){
  rltlist <- list()
  for(i in 1: length(sub_exp_dat)){
     rlt <-  runRstanModelonlocal(sub_exp_dat[[i]])
     rltlist <- list.append(rltlist, rlt)
  }
  saveRDS(rltlist, file = paste0(getwd(), "/modelling/rlt_ALL.rds"))
}
```


### Merge the Result data 
To preprocess the model result data, we merge different model results as two csv files.

```{r}
AllresultList<- readRDS("modelling/rlt_ALL.rds") 
modelresults <- {}
thetalist <- {}
if (needmerge == 1){
  for(i in 1:length(AllresultList)){
     modelresults = rbind(modelresults, AllresultList[[i]]$result) 
     thetalist <- rbind(thetalist, AllresultList[[i]]$theta)
  }
  write.csv(modelresults, file.path(getwd(), "modelling/modelresults.csv"))
  write.csv(thetalist, file.path(getwd(), "modelling/thetalist.csv"))
}
```

###load the data and remove the outliers

```{r}
par_observed <- read.csv('modelling/psy_quickpsy_observed.csv') %>% filter(!((NSub == 10|NSub == 6) & (cond == 'AF'| cond =='DF')))%>% filter(!((NSub == 1) & (cond == 'PS'| cond =='NS')))
modelresults<- read.csv("modelling/modelresults.csv")  %>% filter(!((NSub == 10|NSub == 6) & (cond == 'AF'| cond =='DF')))%>% filter(!((NSub == 1) & (cond == 'PS'| cond =='NS')))
```

### prediction of 'long' response

```{r}
pred_thetalist<- read.csv("modelling/thetalist.csv") 
pred_thetalist$X <-NULL
## probality of 'long' response for experiment 1, 2 and 3 
prob_exp <- read.csv('modelling/prob_exp.csv')
prob_exp$Dur = prob_exp$curDur
prob_exp$curDur <-NULL
prob_exp$obser_prob <-prob_exp$prob 
prob_exp$prob <-NULL


#combine oberserved and predicated probility
m_thetalist = left_join(pred_thetalist, prob_exp, by = c('NSub', 'cond', 'Dur')) 
m_thetalist$numParam = 6
m_thetalist[which(m_thetalist$model %in% c("Two-stage Ensemble Mean","Two-stage Ensemble Mean GM" )), "numParam"] = 9
m_thetalist[which(m_thetalist$model %in% c( "EDA", "EDA GM")), "numParam"] = 10
m_thetalist$err_prob = m_thetalist$Prob- m_thetalist$obser_prob
```

```{r}
#calculate AIC and BIC
mm_thetalist <- m_thetalist %>% dplyr::group_by(model, cond) %>%
  dplyr::summarise(sumerrprob=sum((err_prob)^2), n=n(), numParam = mean(numParam)) %>% 
  dplyr::group_by(model,cond) %>%
  summarise(aicProb= 2 * numParam +  n*log(sumerrprob/n),
            bicProb = n*log(sumerrprob/n) + numParam*log(n))  %>% 
  group_by(model) %>%
  summarise(m_aicProb = mean(aicProb), m_bicProb = mean(bicProb)) 
mm_thetalist
```

### prediction of PSE and JND
```{r}
#combine oberserved and predicated PSEs and JNDs
par_comb = left_join(modelresults, par_observed, by = c('NSub', 'cond')) 
par_comb$errpse <- par_comb$PSEmap-par_comb$pse
par_comb$errjnd <- par_comb$JNDmap-par_comb$jnd
head(par_comb)
```


```{r}
displayModellist <- c("Bisection Model",  "Spacing Model", "Ensemble Mean",  "Two-stage Ensemble Mean", "EDA")
par_comb <- par_comb %>% 
  filter(model %in% displayModellist)
par_comb<- arrange(transform(par_comb , model = factor(model, levels = displayModellist)), model)
par_comb <- arrange(transform(par_comb,
                              cond=factor(cond,levels=c("PS","DF","U-shaped","NS","AF","I T-shaped"))),cond)

par_comb$numParam = 6
par_comb[which(par_comb$model %in% c("Two-stage Ensemble Mean","Two-stage Ensemble Mean GM" )), "numParam"] = 9
par_comb[which(par_comb$model %in% c( "EDA", "EDA GM")), "numParam"] = 10
```


```{r}
#calculate AIC and BIC
mpar_comb <- par_comb %>% dplyr::group_by(model, cond) %>%
  dplyr::summarise(sumerrpse=sum((errpse)^2), n=n(), 
                   sumerrjnd=sum((errjnd)^2), numParam = mean(numParam)) %>% 
  dplyr::group_by(model, cond) %>%
  summarise(aicPse= 2 * numParam +  n*log(sumerrpse/n),
            bicPse = n*log(sumerrpse/n) + numParam*log(n),
            aicJnd= 2 * numParam +  n*log(sumerrjnd/n),
            bicJnd = n*log(sumerrjnd/n) + numParam*log(n), ) 

### show the mean in each model 
m_par <- modelresults %>% group_by(model, cond, NSub) %>%
  summarise(xmean= mean(xmean), xmeanhat= mean(xmeanhat))  %>%
  group_by(model, cond) %>%
  summarise(xmean= mean(xmean), xmeanhat= mean(xmeanhat)) 
m_par
```


## plot figure 7 in manuscript

```{r}
#customize theme
theme_new <- theme_bw() + 
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line=element_line(colour="black"),
        strip.background = element_rect(color = "white", fill = "white"),
        panel.grid = element_blank())
```

```{r}
cbp1 <- c( "#CC79A7", "#F0E442", "#0072B2", "#E69F00", "#D55E00")
plt_ErrorScatter = ggplot(par_comb, aes(errpse, errjnd, color = model, shape = model)) + 
  geom_hline(yintercept = 0, linetype='dashed')+ geom_vline(xintercept = 0, linetype='dashed')+ 
  geom_point() +
  xlab('Prediction error in the PSEs (ms)')+ ylab('Prediction error in the JNDs (ms)')+
  scale_color_manual(values = cbp1) +
  scale_shape_manual(values=c(0, 1, 2, 8, 16))+
  facet_wrap(~cond)+
  theme_new+ theme(legend.position = 'top')

ggsave(paste0("figures/fig7.png"), plt_ErrorScatter, width = 9, height=6)
plt_ErrorScatter
```



## plot figure 6 in manuscript
```{r}
m_parcomb <- par_comb %>% dplyr::group_by(model, cond) %>%
  dplyr::summarise(mPSEmap=mean(PSEmap), pse = mean(pse), mJNDmap=mean(JNDmap),jnd = mean(jnd),
                   merrpse =mean(errpse), merrjnd = mean(errjnd),n=n(), 
                   PSEmap_se = sd(PSEmap)/sqrt(n-1), JNDmap_se = sd(JNDmap)/sqrt(n-1),
                   errpse_se =sd(errpse)/sqrt(n-1), errjnd_se =sd(errjnd)/sqrt(n-1)) 

m_par_observed <- par_observed %>% dplyr::group_by(cond) %>%
  dplyr::summarise(mpse=mean(pse), mjnd= mean(jnd), n=n(), 
                   pse_se =sd(pse)/sqrt(n-1), jnd_se =sd(jnd)/sqrt(n-1)) 
m_par_observed$mPSEmap<-m_par_observed$mpse 
m_par_observed$mJNDmap<-m_par_observed$mjnd 

m_parcomb2 <- arrange(transform(m_parcomb,
             cond=factor(cond,levels=c("PS","DF","U-shaped","NS","AF","I T-shaped"))),cond)


fig_estimation = ggplot(m_parcomb2, aes(x=mPSEmap, y=mJNDmap, color = model, shape = model)) + 
  geom_point(data =m_par_observed, aes(x = mpse, y =mjnd, size=2), width =2, shape =16, alpha = 0.5,  color = 'black') +
  geom_point(data = par_comb, aes(x = pse, y =jnd), alpha = 0.25, color = 'lightgray', shape=16) +
  geom_point() +
  geom_errorbar(aes(ymax=mJNDmap+JNDmap_se, ymin=mJNDmap-JNDmap_se), size=0.6)+
  geom_errorbarh(aes(xmax=mPSEmap+PSEmap_se, xmin=mPSEmap-PSEmap_se),size=0.6)+
  ylab('Observed JNDs (ms)')+xlab('Observed PSEs (ms)') +
  scale_color_manual(values = cbp1) +
  scale_shape_manual(values=c(0, 1, 2, 8, 16))+
  theme_new+ theme(legend.position = 'top') + 
  facet_wrap(.~cond,  ncol=3)+
  scale_size(guide = 'none')

ggsave(paste0("figures/fig6.png"), fig_estimation, width = 9, height=6)
fig_estimation
```

calculate distance to the observed Pses and Jnds
```{r}
m_parcomb2$distance = sqrt((m_parcomb2$mPSEmap -m_parcomb2$pse)^2 +(m_parcomb2$mJNDmap -m_parcomb2$jnd)^2)
mm_parcomb2 <- m_parcomb2 %>% dplyr::group_by(model) %>%
  dplyr::summarise(m_distance = mean(distance)) 
head(mm_parcomb2)
```

### plt AIC together
```{r}
par_comb2 <- left_join(m_parcomb, mpar_comb, by = c('model', 'cond'))  

plt_aicpse<- ggplot(data = par_comb2, aes(cond, aicPse, color = model, fill = model, group =model)) +
  geom_point(position=position_dodge(.25)) + 
  geom_line(position=position_dodge(.25))+
  geom_errorbar(aes(ymax=aicPse+errjnd_se, ymin=aicPse-errjnd_se), width=1,size=0.5, position=position_dodge(.25))+
  xlab('')+ylab('Average AIC of PSE Estimation')+
  theme_new+
  #scale_color_manual(values = cbp1) +
  theme(legend.position = 'bottom') 
plt_aicpse
```
```{r}
plt_aicjnd<- ggplot(data =par_comb2, aes(cond, aicJnd, color = model, fill = model, group =model)) +
  geom_point( position=position_dodge(.25)) + 
  geom_line( position=position_dodge(.25))+
  geom_errorbar(aes(ymax=aicJnd+errjnd_se, ymin=aicJnd-errjnd_se), width=1,size=0.5, position=position_dodge(.25))+
  xlab('')+ylab('Average AIC of JND Estimation')+
  theme_new+
  #scale_color_manual(values = cbp1) +
  theme(legend.position = 'bottom') 
plt_aicjnd
```


### ollapsed across six sets conditions, 
```{r}
meanAIC <- par_comb2 %>% 
  group_by(model) %>%
  summarise(m_aicPse = mean(aicPse), m_aicJnd = mean(aicJnd)) 
meanAIC
```



```{r}
plt_aicpsejnd<- ggarrange(plt_aicpse, plt_aicjnd, common.legend = TRUE, ncol=2, nrow=1)+
  theme(legend.position = 'bottom') 
plt_aicpsejnd
```
