---
title: "Temporal bisection is influenced by ensemble statistics of the stimulus set (Data Analysis Report)"
author: "Xiuna Zhu"
date: "12 Februar 2019"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
source('dataana.R')
```


```{r}
mDist <-  dat_all %>% dplyr::group_by(NSub, cond) %>%
  summarise(m_cDur = mean(curDur), n = dplyr::n(),
            sd_Dur = sd(curDur),
            gm_Dur = gm_mean(curDur),
            cDur_se = sd(curDur)/sqrt(n-1))
mDist
```



# Experiment 1 

positive skew condition (400, 504, 636, 800, 1008, 1270, and 1600 ms)

negative skew condition (400, 730, 992, 1200, 1366, 1496, and 1600 ms)

## Range Frequency Theory

To understand the pattern of results concerning schifts in the temporal bisection point, We have to check the distribution of stimuli within the sets firstly. 
```{r}
sumfreq_exp1_sub1 <-  dat_exp1 %>% filter(NSub == 1) %>% group_by(cond, curDur) %>% summarise(count = n())
count_exp1 <- sum(sumfreq_exp1_sub1$count)/2
sumfreq_exp1_sub1$exp <- 'Exp1'
sumfreq_exp1_sub1$freq <- sumfreq_exp1_sub1$count/count_exp1*100

# rename columns
fig_exp1_sub1_dist <- ggplot(data=sumfreq_exp1_sub1, aes(x=curDur, y=count, fill=cond)) +
  geom_bar(stat="identity", position=position_dodge()) +
  #geom_smooth(method="loess",se = FALSE)+
  xlab('Durations (ms)') + ylab('Counts of trials for each participant') +
  scale_x_continuous(breaks=seq(0, 1600, 200)) +
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +mytheme+ facet_wrap(~cond)

fig_exp1_sub1_dist
```
## plot the distribution of stimulus set
```{r}
mDist_exp1 <-  dat_exp1 %>% filter(NSub == 1) %>% dplyr::group_by(cond) %>%
  summarise(m_cDur = mean(curDur), n = dplyr::n(),
            cDur_se = sd(curDur)/sqrt(n-1))
mDist_exp1
```


```{r}
plot_mDist_exp1 <- ggplot(mDist_exp1,aes(cond, m_cDur, color = cond, fill = cond))+
  geom_bar(stat='identity') +
  geom_errorbar(aes(ymin = m_cDur - cDur_se, ymax = m_cDur + cDur_se), width =0.5) +
  labs(x = " ", y = "Mean of Durations (ms)") +
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = "none", legend.title = element_blank())+
  theme(panel.grid.major=element_line(colour=NA))+
  theme(axis.text.y = element_text(size=26,colour = "black"),
        axis.text.x   = element_text(size=26, colour = "black"),
        axis.title.y  = element_text(size=26, colour = "black"),
        axis.title.x  = element_text(size=26, colour = "black"),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"))

plot_mDist_exp1
```



## fit psychometric functions


```{r fit psychometric functions Exp Spacing}
fits_exp1 = quickpsy(dat_exp1, x = curDur, k =RP, prob = .5,
                     grouping = .(cond, NSub), thresholds = FALSE)
head(fits_exp1$thresholds)
```


```{r}
fits_exp1_all = quickpsy(dat_exp1, x = curDur, k =RP, prob = .5, grouping = .(cond))
fits_exp1_all
```


```{r, fig.cap= 'PSE: Bisection task performance in Experiment Spacing.'}
# plot fitted function
plot_fit_exp1 <- plot(fits_exp1_all) +  
  labs(x = "Durations (ms)", y = "Proportion of 'Long' responses") +
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = c(0.7, 0.2), legend.title = element_blank())

plot_fit_exp1
```



```{r}
aic(fits_exp1_all)
```

```{r}
ypred(fits_exp1_all)
```

=======
##slope
From the equation of psychometric fuction (PF), we can easily obtained the point of subjective equality (PSE, $\alpha$) and just noticeable difference (JND). Notice, the JND is defined by the difference between thresholds P=0.5 and P=0.75, so we have 
$$JND = log3/ \beta$$
Therefore, 

$$\beta = 3 / e^{JND} $$
```{r}
exp1_all_thres<- fits_exp1_all$thresholds
exp1_all_thres$slope = 3/exp(exp1_all_thres$thre/1000) #slope
exp1_all_thres
```


```{r}
exp1_thres<- fits_exp1$thresholds
exp1_thres$slope = 3/exp(exp1_thres$thre/1000) #slope
exp1_thres
```



## list all of the parameter for each subjects
```{r fitted paramters exp1}
par_exp1 = fits_exp1$par %>% 
  dplyr::select(-parinf,-parsup) %>%
  spread(parn, par) %>%   
  rename(pse =p1, jnd = p2)  # rename columns
par_exp1$slope = 3/exp(par_exp1$jnd/1000) #slope

par_exp1
```


```{r average fitted paramters}
mpars_exp1 = par_exp1%>% 
  group_by(cond) %>%
  summarise(m_pse = mean(pse), m_jnd = mean(jnd),  m_slope = mean(slope), n = n(),
            pse_se = sd(pse)/sqrt(n-1), 
            jnd_se = sd(jnd)/sqrt(n-1),
            slope_se = sd(slope)/sqrt(n-1)) 

mpars_exp1
```




=======
##Export for JASP

List all of the parameters for exp1 and export data for JASP
```{r}
exp1_jasp <- par_exp1%>% 
  unite(pse.jnd.slope, pse, jnd, slope)%>%
  spread(cond, pse.jnd.slope)%>%
  separate(`PS`, c("PSC_pse", "PSC_jnd","PSC_slope"), sep = "_")%>%
  separate(`NS`, c("NSC_pse", "NSC_jnd","NSC_slope"), sep = "_")

exp1_jasp
```



## plot PSE
```{r}
plot_pse_exp1 <- ggplot(mpars_exp1,aes(cond, m_pse, color = cond, fill = cond))+
  geom_bar(stat='identity') + 
  geom_errorbar(aes(ymin = m_pse - pse_se, ymax = m_pse + pse_se), width =0.5) +
  geom_signif(comparisons=list(c("PS", "NS")), annotations="*", y_position = 1150, tip_length = 0, vjust=0.4, color = 'black') +
  labs(x = " ", y = "Mean PSE (ms)") +
  coord_cartesian(ylim = c(0,1300)) +
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = "none")

plot_pse_exp1
```

```{r}
plot_pse_exp1_box <- ggplot(par_exp1,aes(x=cond, y=pse, color = cond))+
  geom_boxplot() + 
  geom_jitter(position=position_jitter(0.2))+
  geom_signif(comparisons=list(c("PS", "NS")), annotations="*", y_position = 1350, tip_length = 0, vjust=0.4, color = 'black') +
  labs(x = " ", y = "Mean PSE (ms)") +
  coord_cartesian(ylim = c(500,1400)) +
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = "none")

plot_pse_exp1_box
```

## plot JND
```{r}
plot_jnd_exp1_box <- ggplot(par_exp1,aes(x=cond, y=jnd, color = cond))+
  geom_boxplot() + 
  geom_jitter(position=position_jitter(0.2))+
  labs(x = " ", y = "Mean JND (ms)") +
  coord_cartesian(ylim = c(80,380))+
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) + theme(legend.position = "none")

plot_jnd_exp1_box
```

```{r}
plot_jnd_exp1 <- ggplot(mpars_exp1,aes(cond, m_jnd, color = cond, fill = cond))+
  geom_bar(stat='identity') + 
  geom_errorbar(aes(ymin = m_jnd - jnd_se, ymax = m_jnd + jnd_se), width =0.5) +
  labs(x = " ", y = "Mean JND (ms)") +
  coord_cartesian(ylim = c(0,400))+
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) + theme(legend.position = "none")

plot_jnd_exp1
```


## ANOVA and T-test

```{r}
Anova_exp1_pse<- ezANOVA(data = par_exp1, dv= pse, wid=NSub, within=.(cond))
Anova_exp1_pse
```



```{r}
Anova_exp1_jnd<- ezANOVA(data = par_exp1, dv= jnd, wid=NSub, within=.(cond))
Anova_exp1_jnd
```



```{r}
Anova_exp1_slope<- ezANOVA(data = par_exp1, dv= slope, wid=NSub, within=.(cond))
Anova_exp1_slope
```


# Experiment 2

## Range Frequency Theory

A particular focus is the distribution of stimuli within the sets to be judged.  To understand the pattern of results concerning schifts in the temporal bisection point, We have to check the frequency of the sets firstly. 


```{r}
sumfreq_exp2_sub1 <-  dat_exp2 %>% filter(NSub == 1) %>% group_by(cond, curDur) %>% summarise(count = n()) 
count_exp2 <- sum(sumfreq_exp2_sub1$count)/2
sumfreq_exp2_sub1$exp <- 'Exp2'
sumfreq_exp2_sub1$freq <- sumfreq_exp2_sub1$count/count_exp2*100
fig_exp2_sub1_dist <- ggplot(data=sumfreq_exp2_sub1, aes(x=curDur, y=count, fill=cond)) +
  geom_bar(stat="identity", position=position_dodge()) + 
  xlab('Durations (ms)') + ylab('Counts of trials for each participant') +
  scale_x_continuous(breaks=seq(0, 1600, 200)) +
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +mytheme

fig_exp2_sub1_dist
```


```{r}
mDist_exp2 <-  dat_exp2 %>% filter(NSub == 1) %>% dplyr::group_by(cond) %>%
  summarise(m_cDur = mean(curDur), n = dplyr::n(),
            cDur_se = sd(curDur)/sqrt(n-1))
mDist_exp2
```


```{r}
plot_mDist_exp2 <- ggplot(mDist_exp2,aes(cond, m_cDur, color = cond, fill = cond))+
  geom_bar(stat='identity') +
  geom_errorbar(aes(ymin = m_cDur - cDur_se, ymax = m_cDur + cDur_se), width =0.5) +
  #geom_text(aes(label=paste("(",m_cDur,",",round(cDur_se),")") ),size=8, hjust=0.5, vjust=-2, color = 'black')+
  labs(x = " ", y = " ") +
  #coord_cartesian(ylim = c(0,1600))+
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = "none", legend.title = element_blank())+
  theme(panel.grid.major=element_line(colour=NA))+
  theme(axis.text.y = element_text(size=26,colour = "black"),
        axis.text.x   = element_text(size=26, colour = "black"),
        axis.title.y  = element_text(size=26, colour = "black"),
        axis.title.x  = element_text(size=26, colour = "black"),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")
  )

plot_mDist_exp2
```



## Fit psychometric functions
```{r fit psychometric functions Exp2}
fits_exp2 = quickpsy(dat_exp2, x = curDur, k =RP, prob = .5, grouping = .(cond, NSub))
```


```{r}
fits_exp2_all = quickpsy(dat_exp2, x = curDur, k =RP, 
                         grouping = .(cond))
fits_exp2_all
```

```{r, fig.cap= 'PSE: Bisection task performance in Experiment 2'}
# plot fitted function
plot_fit_exp2 <- plot(fits_exp2_all) + 
  labs(x = "Durations (ms)", y = "Proportion of 'Long' responses") +
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = c(0.7, 0.2), legend.title = element_blank())

plot_fit_exp2
```


## Average fitted paramters and plot
```{r list all of the parameter for each subjects}
par_exp2 = fits_exp2$par %>% 
  dplyr::select(-parinf,-parsup) %>%
  spread(parn, par) %>%   
  rename(pse =p1, jnd = p2)  # rename columns

par_exp2$slope = 3/exp(par_exp2$pse/1000) #add slope

par_exp2
```

```{r}
mpse_exp2 = par_exp2%>% 
  group_by(cond) %>%
  summarise(m_pse = mean(pse), m_jnd = mean(jnd), m_slope = mean(slope), n = n(),
            pse_se = sd(pse)/sqrt(n-1), 
            jnd_se = sd(jnd)/sqrt(n-1),
            slope_se = sd(slope)/sqrt(n-1)) 
mpse_exp2
```

##  Export for JASP

List all of the parameters for Exp2 and export data for JASP
```{r}
exp2_jasp <- par_exp2%>% 
  unite(pse.jnd.slope, pse, jnd, slope)%>%
  spread(cond, pse.jnd.slope)%>%
  separate(DF, c("DF_pse", "DF_jnd","DF_slope"), sep = "_")%>%
  separate(AF, c("AF_pse", "AF_jnd", "AF_slope"), sep = "_")

exp2_jasp
```


## plot PSE
```{r}
plot_pse_exp2 <- ggplot(mpse_exp2,aes(cond, m_pse, color = cond, fill = cond))+
  geom_bar(stat='identity') + 
  geom_errorbar(aes(ymin = m_pse - pse_se, ymax = m_pse + pse_se), width =0.5) +
  geom_signif(comparisons=list(c("DF", "AF")), annotations="***", y_position = 1250, tip_length = 0, vjust=0.4, color = 'black') +
  labs(x = " ", y = "Mean PSE (ms)") +
  coord_cartesian(ylim = c(0,1300))+
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = "none")

plot_pse_exp2
```

```{r}
plot_pse_exp2_box <- ggplot(par_exp2,aes(x=cond, y=pse, color = cond))+
  geom_boxplot() + 
  geom_jitter(position=position_jitter(0.2))+
  geom_signif(comparisons=list(c("DF", "AF")), annotations="***", y_position = 1450, tip_length = 0, vjust=0.4, color = 'black') +
  labs(x = " ", y = "Mean PSE (ms)") +
  coord_cartesian(ylim = c(500,1500))+
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = "none")

plot_pse_exp2_box
```

## plot JND
```{r}
plot_jnd_exp2 <- ggplot(mpse_exp2,aes(cond, m_jnd, color = cond, fill = cond))+
  geom_bar(stat='identity') + 
  geom_errorbar(aes(ymin = m_jnd - jnd_se, ymax = m_jnd + jnd_se), width =0.5) +
  geom_signif(comparisons=list(c("DF", "AF")), annotations="***", y_position = 330, tip_length = 0, vjust=0.4, color = 'black') +
  labs(x = " ", y = "Mean JND (ms)") +
  coord_cartesian(ylim = c(0,350))+
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = "none")

plot_jnd_exp2
```
```{r}
plot_jnd_exp2_box <- ggplot(par_exp2,aes(x=cond, y=jnd, color = cond))+
  geom_boxplot() + 
  geom_jitter(position=position_jitter(0.2)) +
  geom_signif(comparisons=list(c("DF", "AF")), annotations="***", y_position = 310, tip_length = 0, vjust=0.4, color = 'black') +
  labs(x = " ", y = "Mean JND (ms)") +
  coord_cartesian(ylim = c(80,330))+
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = "none")

plot_jnd_exp2_box
```






## ANOVA 

```{r}
Anova_exp2_pse <- ezANOVA(data = par_exp2, dv= pse, wid=NSub, within=.(cond))
Anova_exp2_pse
```


```{r}
Anova_exp2_jnd <- ezANOVA(data = par_exp2, dv= jnd, wid=NSub, within=.(cond))
Anova_exp2_jnd
```


```{r}
Anova_exp2_slope <- ezANOVA(data = par_exp2, dv= slope, wid=NSub, within=.(cond))
Anova_exp2_slope
```

# Experiment 3

## Range Frequency Theory

To understand the pattern of results concerning schifts in the temporal bisection point, We have to check the distribution of stimuli within the sets firstly. 
```{r}
sumfreq_exp3_sub1 <-  dat_exp3 %>% filter(NSub ==1) %>% group_by(cond, curDur) %>% summarise(count = n()) 
# rename columns
sumfreq_exp3_sub1$exp <- 'Exp3'
count_exp3 <- sum(sumfreq_exp3_sub1$count)/2
sumfreq_exp3_sub1$freq <- sumfreq_exp3_sub1$count/count_exp3*100

fig_exp3_sub1_dist <- ggplot(data=sumfreq_exp3_sub1, aes(x=curDur, y=freq, fill=cond)) +
  geom_bar(stat="identity", position=position_dodge()) + 
  xlab('Durations (ms)') + ylab('Counts of trials for each participant') +
  scale_x_continuous(breaks=seq(0, 1600, 200)) +
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +mytheme

fig_exp3_sub1_dist
```

```{r}
mDist_exp3 <-  dat_exp3 %>% filter(NSub == 1) %>% dplyr::group_by(cond) %>%
  summarise(m_cDur = mean(curDur), n = dplyr::n(),
            cDur_se = sd(curDur)/sqrt(n-1))
mDist_exp3
```


```{r}
plot_mDist_exp3 <- ggplot(mDist_exp3,aes(cond, m_cDur, color = cond, fill = cond))+
  geom_bar(stat='identity') +
  geom_errorbar(aes(ymin = m_cDur - cDur_se, ymax = m_cDur + cDur_se), width =0.5) +
  labs(x = " ", y = " ") +
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = "none", legend.title = element_blank())+
  theme(panel.grid.major=element_line(colour=NA))+
  theme(axis.text.y = element_text(size=26,colour = "black"),
        axis.text.x   = element_text(size=26, colour = "black"),
        axis.title.y  = element_text(size=26, colour = "black"),
        axis.title.x  = element_text(size=26, colour = "black"),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"))
plot_mDist_exp3
```


## Fit psychometric functions


```{r fit psychometric functions Exp3}
fits_exp3 = quickpsy(dat_exp3, x = curDur, k =RP, prob = .5,
                     grouping = .(cond, NSub), thresholds = FALSE)
```


```{r}
fits_exp3_all = quickpsy(dat_exp3, x = curDur, k =RP, 
                         grouping = .(cond), thresholds = FALSE)
fits_exp3_all
```



```{r, fig.cap= 'PSE: Bisection task performance in Experiment 3.'}
# plot fitted function
plot_fit_exp3 <- plot(fits_exp3_all) +  
  labs(x = "Durations (ms)", y = "Proportion of 'Long' responses") +
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = c(0.7, 0.2), legend.title = element_blank())

plot_fit_exp3
```



## List all of the parameter for each subjects


```{r}
par_exp3 = fits_exp3$par %>% 
  dplyr::select(-parinf,-parsup) %>%
  spread(parn, par) %>%   
  rename(pse =p1, jnd = p2)  # rename columns

par_exp3$slope = 3/exp(par_exp3$pse/1000) #add slope

par_exp3
```




```{r fitted paramters Exp3}
mpars_exp3 = par_exp3%>% 
  group_by(cond) %>%
  summarise(m_pse = mean(pse), m_jnd = mean(jnd), m_slope = mean(slope), n = n(),pse_se = sd(pse)/sqrt(n-1), jnd_se = sd(jnd)/sqrt(n-1),slope_se = sd(slope)/sqrt(n-1))

mpars_exp3
```


##Export for JASP

List all of the parameters for Exp3 and export data for JASP
```{r}
exp3_jasp <- par_exp3%>% 
  unite(pse.jnd.slope, pse, jnd, slope)%>%
  spread(cond, pse.jnd.slope)%>%
  separate(`U-shaped`, c("U_pse", "U_jnd", "U_slope"), sep = "_")%>%
  separate(`I T-shaped`, c("B_pse", "B_jnd", "B_slope"), sep = "_")

exp3_jasp
```


## plot PSE
```{r}
plot_pse_exp3 <- ggplot(mpars_exp3,aes(cond, m_pse, color = cond, fill = cond))+
  geom_bar(stat='identity') + 
  geom_errorbar(aes(ymin = m_pse - pse_se, ymax = m_pse + pse_se), width =0.5) +
  coord_cartesian(ylim = c(0,1300)) +
  labs(x = " ", y = "Mean PSE (ms)") +
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = "none", legend.title = element_blank())
plot_pse_exp3
```

```{r}
plot_pse_exp3_box <- ggplot(par_exp3,aes(x=cond, y=pse, color = cond))+
  geom_boxplot() + 
  geom_jitter(position=position_jitter(0.2))+
  coord_cartesian(ylim = c(500,1300)) +
  labs(x = " ", y = "Mean PSE (ms)") +
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = "none", legend.title = element_blank())
plot_pse_exp3_box
```

## plot JND
```{r}
plot_jnd_exp3 <- ggplot(mpars_exp3,aes(cond, m_jnd, color = cond, fill = cond))+
  geom_bar(stat='identity') + 
  geom_errorbar(aes(ymin = m_jnd - jnd_se, ymax = m_jnd + jnd_se), width =0.5) +
  coord_cartesian(ylim = c(0,300))+
  geom_signif(comparisons=list(c("U-shaped", "I T-shaped")), annotations="***", y_position = 250, tip_length = 0, vjust=0.4, color = 'black') +
  labs(x = " ", y = "Mean JND (ms)") +
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = "none")
plot_jnd_exp3
```

```{r}
plot_jnd_exp3_box <- ggplot(par_exp3,aes(x=cond, y=jnd, color = cond))+
  geom_boxplot() + 
  geom_jitter(position=position_jitter(0.2))+
  coord_cartesian(ylim = c(0,400))+
  geom_signif(comparisons=list(c("U-shaped", "I T-shaped")), annotations="***", y_position = 380, tip_length = 0, vjust=0.4, color = 'black') +
  labs(x = " ", y = "Mean JND (ms)") +
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = "none")
plot_jnd_exp3_box
```




## ANOVA

```{r}
Anova_exp3_pse<- ezANOVA(data = par_exp3, dv= pse, wid=NSub, within=.(cond))
Anova_exp3_pse
```



```{r}
Anova_exp3_jnd<- ezANOVA(data = par_exp3, dv= jnd, wid=NSub, within=.(cond))
Anova_exp3_jnd
```



```{r}
Anova_exp3_slope<- ezANOVA(data = par_exp3, dv= slope, wid=NSub, within=.(cond))
Anova_exp3_slope
```

# figures in manuscript

## plot figure 1 in manuscript

```{r}
fig_exp1_sub1_dist2 <- ggplot(data=sumfreq_exp1_sub1, aes(x=curDur, y=freq, fill=cond, color = cond)) +
  geom_bar(stat="identity", position=position_dodge(),width = 3) + 
  geom_point()+
  xlab('') + ylab('Prob. (%)') +
  scale_x_continuous(breaks=seq(0, 1600, 200)) +
  scale_y_continuous(breaks=seq(0, 50, 5)) +
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = "none", legend.title = element_blank()) + facet_wrap(~cond)

fig_exp2_sub1_dist_2 <- ggplot(data=sumfreq_exp2_sub1, aes(x=curDur, y=freq, fill=cond, color = cond)) +
  geom_bar(stat="identity", position=position_dodge(), width = 3) + 
  geom_point()+
  scale_x_continuous(breaks=seq(0, 1600, 200)) +
  scale_y_continuous(breaks=seq(0, 50, 10)) +
  xlab('') + ylab('Prob. (%)') +
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = 'none', legend.title = element_blank()) + facet_wrap(~cond)

fig_exp3_sub1_dist2 <- ggplot(data=sumfreq_exp3_sub1, aes(x=curDur, y=freq, fill=cond, color = cond)) +
  geom_bar(stat="identity", position=position_dodge(), width = 3) + 
  geom_point()+
  xlab('Durations (ms)') + ylab('Prob. (%)') +
  scale_x_continuous(breaks=seq(0, 1600, 200)) +
  scale_y_continuous(breaks=seq(0, 50, 10)) +
  scale_color_manual(values = c('gray','black')) +
  scale_fill_manual(values = c('gray','black')) +
  theme(legend.position = "none", legend.title = element_blank())+ facet_wrap(~cond)

plot_grid(fig_exp1_sub1_dist2, fig_exp2_sub1_dist_2, fig_exp3_sub1_dist2,  ncol = 1, labels = c("A", "B", "C"), rel_heights = c(3,3,3))
```



## plot Figure 2 in manuscript
```{r}
plot_grid(plot_fit_exp1, plot_pse_exp1, plot_jnd_exp1,  nrow = 1, labels = c("A", "B", "C"), rel_widths = c(4,3,3))
```

```{r}
fig2 <- plot_grid(plot_fit_exp1, plot_pse_exp1_box, plot_jnd_exp1_box,  nrow = 1, labels = c("A", "B", "C"), rel_widths = c(4,3,3))
```

## plot Figure 3 in manuscript
```{r}
plot_grid(plot_fit_exp2, plot_pse_exp2, plot_jnd_exp2,  nrow = 1, labels = c("A", "B", "C"), rel_widths = c(4,3,3))
```

```{r}
fig3 <- plot_grid(plot_fit_exp2, plot_pse_exp2_box, plot_jnd_exp2_box,  nrow = 1, labels = c("A", "B", "C"), rel_widths = c(4,3,3))
```

## plot Figure 4 in manuscript
```{r}
plot_grid(plot_fit_exp3, plot_pse_exp3, plot_jnd_exp3,  nrow = 1, labels = c("A", "B", "C"), rel_widths = c(4,3,3))
```

```{r}
fig4 <- plot_grid(plot_fit_exp3, plot_pse_exp3_box, plot_jnd_exp3_box,  nrow = 1, labels = c("A", "B", "C"), rel_widths = c(4,3,3))
```



# Model Results

## load the Model result

```{r}
#customize theme
theme_new <- theme_bw() + 
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line=element_line(colour="black"),
        strip.background = element_rect(color = "white", fill = "white"),
        panel.grid = element_blank())

models <- c('model1', 'model2','model3', 'model4','model5')
expDat <- list(dat_exp1, dat_exp2, dat_exp3)
#load the data and remove the outliers

par_observed <- rbind(rbind(par_exp1, par_exp2), par_exp3)
par_observed <- par_observed %>% filter(!((NSub == 10|NSub == 6 ) & (cond == 'AF'| cond =='DF')))%>% filter(!((NSub == 1) & (cond == 'PS'| cond =='NS')))
modelresults<- read.csv("../data/modelresults.csv")  %>% filter(!((NSub == 10|NSub == 6) & (cond == 'AF'| cond =='DF')))%>% filter(!((NSub == 1) & (cond == 'PS'| cond =='NS')))
```

```{r}
displayModellist <- c("Bisection Model",  "Spacing Model", "Ensemble Mean",  "Two-stage Ensemble Mean", "EDA")
#combine oberserved and predicated PSEs and JNDs
par_comb = left_join(modelresults, par_observed, by = c('NSub', 'cond')) 
par_comb$errpse <- par_comb$PSEmap-par_comb$pse
par_comb$errjnd <- par_comb$JNDmap-par_comb$jnd
par_comb$model = factor(par_comb$model, labels = displayModellist)
head(par_comb)

```



```{r}
#calculate AIC and BIC
numParam <- 3
mpar_comb <- par_comb %>% dplyr::group_by(model, cond) %>%
  dplyr::summarise(sumerrpse=sum((errpse)^2), n=n(), 
                   sumerrjnd=sum((errjnd)^2)) %>% 
  dplyr::group_by(model, cond) %>%
  summarise(aicPse= 2 * numParam +  n*log(sumerrpse/n),
            bicPse = n*log(sumerrpse/n) + numParam*log(n),
            aicJnd= 2 * numParam +  n*log(sumerrjnd/n),
            bicJnd = n*log(sumerrjnd/n) + numParam*log(n), ) 

### show the mean in each model 
m_par <- modelresults %>% group_by(model, cond, NSub) %>%
  summarise(xmean= mean(xmean), xmeanhat= mean(xmeanhat))  %>%
  group_by(model, cond) %>%
  summarise(xmean= mean(xmean), xmeanhat= mean(xmeanhat)) 
```


## plot figure 7 in manuscript
```{r}
par_comb <- arrange(transform(par_comb,
                              cond=factor(cond,levels=c("PS","DF","U-shaped","NS","AF","I T-shaped"))),cond)

cbp1 <- c( "#CC79A7", "#F0E442", "#0072B2", "#E69F00", "#D55E00")
plt_ErrorScatter = ggplot(par_comb, aes(errpse, errjnd, color = model, shape = model)) + 
  geom_hline(yintercept = 0, linetype='dashed')+ geom_vline(xintercept = 0, linetype='dashed')+ 
  geom_point() +
  xlab('Prediction error in the PSEs (ms)')+ ylab('Prediction error in the JNDs (ms)')+
  scale_color_manual(values = cbp1) +
  scale_shape_manual(values=c(0, 1, 2, 8, 16))+
  facet_wrap(~cond)+
  theme_new+ theme(legend.position = 'top')

plt_ErrorScatter
```



## plot figure 6 in manuscript
```{r}
m_parcomb <- par_comb %>% dplyr::group_by(model, cond) %>%
  dplyr::summarise(mPSEmap=mean(PSEmap), pse = mean(pse), mJNDmap=mean(JNDmap),jnd = mean(jnd),
                   merrpse =mean(errpse), merrjnd = mean(errjnd),n=n(), 
                   PSEmap_se = sd(PSEmap)/sqrt(n-1), JNDmap_se = sd(JNDmap)/sqrt(n-1),
                   errpse_se =sd(errpse)/sqrt(n-1), errjnd_se =sd(errjnd)/sqrt(n-1)) 

m_par_observed <- par_observed %>% dplyr::group_by(cond) %>%
  dplyr::summarise(mpse=mean(pse), mjnd= mean(jnd), n=n(), 
                   pse_se =sd(pse)/sqrt(n-1), jnd_se =sd(jnd)/sqrt(n-1)) 
m_par_observed$mPSEmap<-m_par_observed$mpse 
m_par_observed$mJNDmap<-m_par_observed$mjnd 

m_parcomb2 <- arrange(transform(m_parcomb,
             cond=factor(cond,levels=c("PS","DF","U-shaped","NS","AF","I T-shaped"))),cond)


fig_estimation = ggplot(m_parcomb2, aes(x=mPSEmap, y=mJNDmap, color = model, shape = model)) + 
  geom_point(data =m_par_observed, aes(x = mpse, y =mjnd, size=2), width =2, shape =16, alpha = 0.5,  color = 'black') +
  geom_point(data = par_comb, aes(x = pse, y =jnd), alpha = 0.25, color = 'lightgray', shape=16) +
  geom_point() +
  geom_errorbar(aes(ymax=mJNDmap+JNDmap_se, ymin=mJNDmap-JNDmap_se), size=0.6)+
  geom_errorbarh(aes(xmax=mPSEmap+PSEmap_se, xmin=mPSEmap-PSEmap_se),size=0.6)+
  ylab('Observed JNDs (ms)')+xlab('Observed PSEs (ms)') +
  scale_color_manual(values = cbp1) +
  scale_shape_manual(values=c(0, 1, 2, 8, 16))+
  theme_new+ theme(legend.position = 'top') + 
  facet_wrap(.~cond,  ncol=3)+
  scale_size(guide = 'none')

fig_estimation
```

